Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-02-27 resex.tex
Revised Section V on numerical simulations

For the preparation and interpretation of the experiments two different types of simulations were performed:
\begin{enumerate}
	\item tracking of a Gaussian distribution, referred to as ``distribution tracking" in this paper, to obtain loss rates and emittance growth,
	\item Frequency map analysis (FMA) for the visualization of resonances~\cite{fmalaskar}.
\end{enumerate}
For both simulation types, the tracking code Lifetrac \cite{lifetrac} was used. The simulation parameters are summarized in Table~\ref{tab:sim_param}. Further details on the simulations are given in Refs.~\cite{md_sim_hel_res_ex_fitterer,resexmd2017}.
\begin{table}[h]
	\caption{\label{tab:sim_param}%
		Summary of simulation parameters for the distribution tracking and FMA analysis. For details see \cite{md_sim_hel_res_ex_fitterer,resexmd2017}.
	}
	\begin{ruledtabular}
		\begin{tabular}{lcc}
			Parameter & distribution tracking & FMA \\
			\colrule
			beam &\multicolumn{2}{c}{Beam~1} \\
			beam energy &\multicolumn{2}{c}{450 GeV} \\
			emittance & $3.5~\mu$m& $2.5~\mu$m\\
			$4\sigma$ bunch length & \multicolumn{2}{c}{1.3~ns}\\
			$1\sigma$ bunch length & \multicolumn{2}{c}{9.7~cm}\\
			particle & 6D Gaussian & equally spaced grid\\
			distribution &  distribution & in $x,y$ up to $10~\sigma$\\
			&  ($10^4$ particles) & with $\frac{\Delta p}{p_0}=0$\\
			turns tracked & $10^6$ turns & $10^4$ turns \\\hline
			optics & \multicolumn{2}{c}{2016 or 2017 injection optics,}\\
			& \multicolumn{2}{c}{$\beta_{\mathrm{IP1/5}}^*=11$~m}\\
			machine  & standard errors & no errors \\
			imperfections &with $a_1=b_1=0$\footnote{Orbit errors are disabled due to different implementation of the $a_1,b_1$ errors in Lifetrac and MAD-X. $b_2$ errors are adjusted to yield an average (over 60 seeds) peak $\beta$-beat of 15\% as expected from optics measurements in the LHC.} &  \\
			octupoles  & \multicolumn{2}{c}{$I_{\mathrm{MOF}}=+19.6~\mathrm{A}$, $I_{\mathrm{MOD}}=-19.6~\mathrm{A}$}\\
			tune $(Q_x,Q_y)$ & \multicolumn{2}{c}{(64.28,59.31) for 2016,}\\
			& \multicolumn{2}{c}{(62.27,60.295) for 2017}\\
			chromaticity & \multicolumn{2}{c}{(+15,+15)}\\
			$(Q'_x,Q'_y)$ & & \\\hline
			transv. aperture & $5.7~\sigma$ & - \\
			long. aperture & $10~\sigma$ & - \\
		\end{tabular}
	\end{ruledtabular}
\end{table}

>>>>

\begin{table*}
  \caption{Summary of parameters used in numerical simulations of
    distribution tracking and frequency-map analysis (FMA). Further
    details can be found in Refs.~\cite{md_sim_hel_res_ex_fitterer,
      resexmd2017}.}
  \label{tab:sim_param}
  \begin{ruledtabular}
    \begin{tabular}{lcc}
      Parameter & distribution & FMA \\
      \colrule
      beam &\multicolumn{2}{c}{Beam~1} \\
      beam energy &\multicolumn{2}{c}{450 GeV} \\
      normalized emittance & \q{3.5}{\mu m} & \q{2.5}{\mu m} \\
      $4\sigma$ bunch length & \multicolumn{2}{c}{1.3~ns} \\
      $1\sigma$ bunch length & \multicolumn{2}{c}{9.7~cm} \\
      particle distribution & \parbox{0.4\textwidth}{6D Gaussian
                              distribution with $10^4$ particles}
                               & \parbox{0.4\textwidth}{equally spaced
                                 grid in $x, y$ up to $10\sigma$, with
                                 $(\Delta p / p_0) = 0$} \\
      turns tracked & $10^6$ & $10^4$ \\
      \hline
      optics & \multicolumn{2}{c}{2016 or 2017 injection optics, with
               $\beta^* = \q{11}{m}$ at IP1 and IP5} \\
      machine imperfections & standard errors, with $a_1 = b_1 =
                              0$\footnote{Orbit
                              errors are disabled due to
                              different implementation of the
                              $a_1, b_1$ coefficients in Lifetrac and
                              MAD-X. $b_2$ errors are adjusted to
                              yield an average
                              peak $\beta$-beat of 15\% over 60~seeds, as
                              observed in optics measurements
                              in the LHC.} & no errors \\
      octupoles  & \multicolumn{2}{c}{$I_{\mathrm{MOF}} =
                   \q{+19.6}{A}$, $I_{\mathrm{MOD}} = \q{-19.6}{A}$} \\
      tunes $(Q_x, Q_y)$ & \multicolumn{2}{c}{(64.28, 59.31) for 2016,
                           (62.27, 60.295) for 2017} \\
      chromaticities $(Q'_x, Q'_y)$ & \multicolumn{2}{c}{(+15, +15)} \\
      \hline
      transverse aperture & $5.7\sigma$ &  \\
      longitudinal aperture & $10\sigma$ &  \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

For the preparation and interpretation of the experiments, two
different types of simulations were performed:
%
\begin{itemize}
\item tracking of a Gaussian distribution, referred to as
  `distribution tracking' in this paper, to obtain particle loss rates
  and emittance evolution;
\item frequency-map analysis (FMA), to visualize the location and
  intensity of resonances~\cite{fmalaskar}.
\end{itemize}
%
For both simulation types, the tracking code Lifetrac~\cite{lifetrac}
was used. The simulation parameters are summarized in
Table~\ref{tab:sim_param}. Further details are given in
Refs.~\cite{md_sim_hel_res_ex_fitterer, resexmd2017}.

Simulation results are discussed below in Section~\ref{sec:simex}
together with the experimental results to enhance the understanding
and interpretation of the models and observations.
